### 2016-12-15 ms/hardcoded/ms.tex
misc
made some suggestions to the intro

\def\extras{
  \begin{itemize}
  \item Submitted as a Letter
  \item Abstract word count: 136
  \item Main text word count: 4680
  \item Number of references: 67
  \item Number of figures: 6
  \item Author contributions: CK designed the study, LCP and CK
    collected data, LCP and MPG analyzed output data.  LCP wrote the
    first draft of the manuscript, and all authors contributed to
    revisions.
  \item Data accessibility statement: Data will de depositied in Dryad
    upon publication
  \end{itemize}
}

@@

\newcommand{\mstitlepage}{
  \paragraph{Running head:} \textsc{\runninghead}
  % \parindent=0pt
  \begin{center}%
    {\LARGE \title \par}%
    \vskip 3em%
    {\large
      \lineskip .75em%
      \begin{tabular}[t]{c}%
        \author
      \end{tabular}\par}%
    \vskip 1.5em%
  \end{center}\par
  \affiliation
}
\clearpage

@@

>>>>

\def\extras{
\clearpage
  \begin{itemize}
  \item Submitted as a Letter
  \item Abstract word count: 136
  \item Main text word count: 4680
  \item Number of references: 67
  \item Number of figures: 6
  \item Author contributions: CK designed the study, LCP and CK
    collected data, LCP and MPG analyzed output data.  LCP wrote the
    first draft of the manuscript, and all authors contributed to
    revisions.
  \item Data accessibility statement: Data will de depositied in Dryad
    upon publication
  \end{itemize}
}

@@

\newcommand{\mstitlepage}{
  \paragraph{Running head:} \textsc{\runninghead}
  \parindent=0pt
  \begin{center}
    {\LARGE \title \par}
    \vskip 3em
    {\large
      \lineskip .75em
      \begin{tabular}[t]{c}
        \author
      \end{tabular}\par}
    \vskip 1.5em
  \end{center}\par
  \affiliation
  \extras
}
\clearpage

@@

1) Stability x persistence x community assembly - maybe the easiest part to put a theory. [H4]

2) Link assembly to restoration and ecosystem services, biodiversity crisis (input the former first paragraph). [H4]

3) Focus on specific species in this paragraph, maybe link to niche theory? Mention \cite{kaiser2010robustness, macleod2016measuring} to link species change in interactions (rewire) to their persistence and temporal variation; say that we want to restore habitats that are robust and persistent through time. However, the relationship between species persistence across years and their role in community assembly is still unclear.  [H3 and H4]

4) Paragraph that starts with "Understanding network assembly..." [H1 and H2]

5) Paragraph on changing points; mention the control and the non-assembly hedgerows here [H1 and H2]

6) Maybe rephrase the last paragraph to more question driven statements?
We tested four theoretically motivated hypothesis exploring the process of community assembly using a eight-year
dataset of plant-pollinator network development following hedgerow
installment in the highly simplified and intensively managed
agricultural landscape of California's Central Valley. First,
we determine whether network assembly was punctuated by significant
reorganizations of interactions, and if assembling networks presented more change than the control, non-assembly hedgerows. We next tested whether the species
that are most variable in their network position --- and thus
important contributors to network reorganizations --- are less
persistent and connected species, as would be expected by preferential
attachment. To further explore the mechanisms underlying the temporal
dynamics of the networks, also we examine patterns in the species and
interaction temporal turnover. Finally, we investigate whether
networks assemble toward predictable interaction patterns, and the
ramifications for the robustness of the networks.
